### 2024-06-19 manuscript.Rmd
added default prefix info
add links to sources

authornote: |
  Please address correspondence to: Prof. Dr. Andreas M. Brandmaier, Rüdesheimerstr. 50, 14197 Berlin, Germany. Email: andreas.brandmaier@medicalschool-berlin.de

@@

- reproducibleRchunks.digits: This is the number of digits for rounding of numbers and controls the numeric precision of the reproducibility checks. By default, this is $8$.
- reproducibleRchunks.filetype: This is the type of data storage. Currently, we only support the 'json' format; however, this leaves room for other formats to be supported in future. 
- reproducibleRchunks.hashing: Boolean. Indicates whether fingerprints should be used (default) or raw values should be stored.
- reproducibleRchunks.hashing_algorithm: This is the hashing algorithm, which is used to generate fingerprints of variable contents. By default, the algorithm offered by the `digest` package are used.
- reproducibleRchunks.templates: A list with keys corresponding to pandoc output formats and values to templates for formatting the reproducibility reports. See below for more details.

>>>>

authornote: |
  Please address correspondence to: Prof. Dr. Andreas M. Brandmaier, Rüdesheimerstr. 50, 14197 Berlin, Germany. Email: andreas.brandmaier@medicalschool-berlin.de.
  The R package described in this article can be downloaded from https://github.com/brandmaier/reproducibleRchunks. The manuscript source code is available at https://github.com/brandmaier/reproducibleRchunks-manuscript.

@@

- reproducibleRchunks.digits: This is the number of digits for rounding of numbers and controls the numeric precision of the reproducibility checks. By default, this is $8$.
- reproducibleRchunks.filetype: This is the type of data storage. Currently, we only support the 'json' format; however, this leaves room for other formats to be supported in future. 
- reproducibleRchunks.hashing: Boolean. Indicates whether fingerprints should be used (default) or raw values should be stored.
- reproducibleRchunks.hashing_algorithm: This is the hashing algorithm, which is used to generate fingerprints of variable contents. By default, the algorithm offered by the `digest` package are used.
- reproducibleRchunks.templates: A list with keys corresponding to pandoc output formats and values to templates for formatting the reproducibility reports. See below for more details.
- reproducibleRchunks.prefix: This is the prefix for the file containing reproducibility information. The filename will always contain the name of the R Markdown file and the chunk name separated by an underscore. The default prefix is `.repro`.
